---
title: "R Notebook for non-parametric analysis"
author: Geiser C. Challco <geiser@alumni.usp.br>
comment: Author - Geiser C. Challco <geiser@alumni.usp.br>
         
         This code is distributed in the hope that it will be useful,
         but WITHOUT ANY WARRANTY; without even the implied warranty of
         MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
         GNU General Public License for more details.
         
         You should have received a copy of the GNU General Public License.
         If not, see <https://www.gnu.org/licenses/>.
output:
  word_document:
    toc: true
  html_document:
    toc: true
  github_document:
    toc: true
fontsize: 10pt
---

## Install and Load Packages

```{r include=FALSE}
if (!'remotes' %in% rownames(installed.packages())) install.packages('remotes')
if (!"rshinystatistics" %in% rownames(installed.packages())) {
  remotes::install_github("geiser/rshinystatistics")
} else if (packageVersion("rshinystatistics") < "0.0.0.9900") {
  remotes::install_github("geiser/rshinystatistics")
}

wants <- c('readxl','dplyr','rstatix','ggplot2','ggpubr','ggpp')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])
if (!"dmetar" %in% rownames(installed.packages())) {
  remotes::install_github("MathiasHarrer/dmetar")
}

library(rshinystatistics)

library(readxl)
library(plyr)
library(dplyr)
library(rstatix)
library(ggplot2)
library(ggpubr)
library(ggpp)
library(tidyr)

dat <- read_excel("../data/data.xlsx", sheet = "data")

dat$Group <- factor(dat$Group, c("Ctr.A","Ctr.B","Exp"))

dat <- dat[!is.na(dat$pre.score) & !is.na(dat$pos.score),]

```

## Identify the best pre-test and post-test regression

**Legend**:

-   *irt.cc*: estimated ability using concurrent calibration (fixing IRT parameters)
-   *irt.em.norm*: estimated ability using equation mode and normalizing these values - IRT parameters are calculated based on previous and current data


```{r}
values = c("score","irt.cc","irt.em.norm")
lvalues = as.list(values); names(lvalues) = values

do.call(rbind, lapply(lvalues, FUN = function(x) {
  md = summary(lm(as.formula(paste0("pos.",x,"~","pre.",x)), data = dat))
  cbind(md$coefficients, `R2` = md$r.squared, `SSR` = sum(md$residuals^2))
}))
```

**Normality test** 

```{r}
(do.call(rbind, lapply(c(paste0("pre.",values),paste0("pos.",values)), FUN = function(x) {
  cbind(var=x, rshinystatistics::normality.test(dat[[x]]))
})))
```



**Note**: Based the linear regression "Y = a + bX," the best measure that should be used to compare pre- and post-test data is "irt.em.norm".

```{r}
ggscatter(dat, x = "pre.score", y = "pos.score", size = 1, add = "reg.line") +
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"))
  )
```

```{r}
ggscatter(dat, x = "pre.irt.cc", y = "pos.irt.cc", size = 1, add = "reg.line") +
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"))
  )
```


```{r}
ggscatter(dat, x = "pre.irt.em.norm", y = "pos.irt.em.norm", size = 1, add = "reg.line") +
  stat_regline_equation(
    aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"))
  )
```

```{r}
values = c("score","irt.em.norm")
lvalues = as.list(values); names(lvalues) = values
```


## Evaluating H1a (null)

H1a (null): Students who participated in scenarios without our proposed ITS and without training (control group A) have the same mean score/ability in both the pre-test and post-test. **Note**: *Limoeiro - PE*

```{r include=FALSE}
sdat = dat[which(dat$Group == "Ctr.A"),]

wlx.md <- lapply(lvalues, FUN = function(x) {
  pdat <- tidyr::pivot_longer(sdat[,c("ID",paste0("pre.",x),paste0("pos.",x))],
                              cols = ends_with(x), names_to = "time")
  add_significance(wilcox_test(pdat, value ~ time, paired = T, alternative = "greater", detailed = T))
})

df = do.call(rbind, wlx.md)
(df = df[,c("group1","group2","n1","n2","estimate","statistic","p","p.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```

```{r include=FALSE}
df <- lapply(lvalues, FUN = function(x) {
  df = pivot_longer(sdat, cols = c(paste0("pre.",x), paste0("pos.",x)),
                    names_to = "time")
  df$time = factor(df$time, c(paste0("pre.",x), paste0("pos.",x)))
  df
})

df.sum <- lapply(lvalues, FUN = function(x) {
  get_summary_stats(group_by(df[[x]],time)[,c("time","value")])
})
(do.call(rbind, df.sum))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(do.call(rbind, df.sum))
```

```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  df[[x]]$xj <- jitter(as.numeric(df[[x]]$time), amount=.1)
  df[[x]]$yj <- jitter(df[[x]]$value, amount = .01)
  
  pwc <- add_xy_position(wlx.md[[x]], fun = "mean_ci", step.increase=3.5)

  ggline(df.sum[[x]], x="time", y="mean", palette="jco", size=0.75) +
    geom_errorbar(aes_string(ymin="mean-ci", ymax="mean+ci"), width=0.1, size = 1) +
    geom_point(data = df[[x]], aes_string(x="xj",y="yj",colour="time"), size = 0.75) +
    geom_line(data = df[[x]], aes(x=xj, y =yj, group=ID), color = "gray", size = 0.25) +
    stat_pvalue_manual(pwc, hide.ns = F, label = "p = {p}") +
    ylab(paste0(x, "(ability)")) + xlab("")
})
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```




## Evaluating H1b (null)

H1b (null): Students who participated in scenarios without our proposed ITS and with training (control group B) have the same mean score/ability in both the pre-test and post-test.

```{r include=FALSE}
sdat = dat[which(dat$Group == "Ctr.B"),]

wlx.md <- lapply(lvalues, FUN = function(x) {
  pdat <- tidyr::pivot_longer(sdat[,c("ID",paste0("pre.",x),paste0("pos.",x))],
                              cols = ends_with(x), names_to = "time")
  add_significance(wilcox_test(pdat, value ~ time, paired = T, alternative = "greater", detailed = T))
})

df = do.call(rbind, wlx.md)
(df = df[,c("group1","group2","n1","n2","estimate","statistic","p","p.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```

```{r include=FALSE}
df <- lapply(lvalues, FUN = function(x) {
  df = pivot_longer(sdat, cols = c(paste0("pre.",x), paste0("pos.",x)),
                    names_to = "time")
  df$time = factor(df$time, c(paste0("pre.",x), paste0("pos.",x)))
  df
})

df.sum <- lapply(lvalues, FUN = function(x) {
  get_summary_stats(group_by(df[[x]],time)[,c("time","value")])
})
(do.call(rbind, df.sum))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(do.call(rbind, df.sum))
```

```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  df[[x]]$xj <- jitter(as.numeric(df[[x]]$time), amount=.1)
  df[[x]]$yj <- jitter(df[[x]]$value, amount = .01)
  
  pwc <- add_xy_position(wlx.md[[x]], fun = "mean_ci", step.increase=3.5)

  ggline(df.sum[[x]], x="time", y="mean", palette="jco", size=0.75) +
    geom_errorbar(aes_string(ymin="mean-ci", ymax="mean+ci"), width=0.1, size = 1) +
    geom_point(data = df[[x]], aes_string(x="xj",y="yj",colour="time"), size = 0.75) +
    geom_line(data = df[[x]], aes(x=xj, y =yj, group=ID), color = "gray", size = 0.25) +
    stat_pvalue_manual(pwc, hide.ns = F, label = "p = {p}") +
    ylab(paste0(x, "(ability)")) + xlab("")
})
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```



### Sorocaba - SP :: Evaluating H1b (null)

```{r include=FALSE}
sdat = dat[which(dat$Group == "Ctr.B" & dat$Town == "Sorocaba - SP"),]

wlx.md <- lapply(lvalues, FUN = function(x) {
  pdat <- tidyr::pivot_longer(sdat[,c("ID",paste0("pre.",x),paste0("pos.",x))],
                              cols = ends_with(x), names_to = "time")
  add_significance(wilcox_test(pdat, value ~ time, paired = T,
                               alternative = "greater", detailed = T))
})

df = do.call(rbind, wlx.md)
(df = df[,c("group1","group2","n1","n2","estimate","statistic","p","p.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```

```{r include=FALSE}
df <- lapply(lvalues, FUN = function(x) {
  df = pivot_longer(sdat, cols = c(paste0("pre.",x), paste0("pos.",x)), names_to = "time")
  df$time = factor(df$time, c(paste0("pre.",x), paste0("pos.",x)))
  df
})

df.sum <- lapply(lvalues, FUN = function(x) {
  get_summary_stats(group_by(df[[x]],time)[,c("time","value")])
})
(do.call(rbind, df.sum))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(do.call(rbind, df.sum))
```

```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  df[[x]]$xj <- jitter(as.numeric(df[[x]]$time), amount=.1)
  df[[x]]$yj <- jitter(df[[x]]$value, amount = .01)
  
  pwc <- add_xy_position(wlx.md[[x]], fun = "mean_ci", step.increase=3.5)

  ggline(df.sum[[x]], x="time", y="mean", palette="jco", size=0.75) +
    geom_errorbar(aes_string(ymin="mean-ci", ymax="mean+ci"), width=0.1, size = 1) +
    geom_point(data = df[[x]], aes_string(x="xj",y="yj",colour="time"), size = 0.75) +
    geom_line(data = df[[x]], aes(x=xj, y =yj, group=ID), color = "gray", size = 0.25) +
    stat_pvalue_manual(pwc, hide.ns = F, label = "p = {p}") +
    ylab(paste0(x, "(ability)")) + xlab("")
})
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```



```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```


### Limoeiro - PE :: Evaluating H1b (null)

```{r include=FALSE}
sdat = dat[which(dat$Group == "Ctr.B" & dat$Town == "Limoeiro - PE"),]

wlx.md <- lapply(lvalues, FUN = function(x) {
  pdat <- tidyr::pivot_longer(sdat[,c("ID",paste0("pre.",x),paste0("pos.",x))],
                              cols = ends_with(x), names_to = "time")
  add_significance(wilcox_test(pdat, value ~ time, paired = T,
                               alternative = "greater", detailed = T))
})

df = do.call(rbind, wlx.md)
(df = df[,c("group1","group2","n1","n2","estimate","statistic","p","p.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```

```{r include=FALSE}
df <- lapply(lvalues, FUN = function(x) {
  df = pivot_longer(sdat, cols = c(paste0("pre.",x), paste0("pos.",x)),
                    names_to = "time")
  df$time = factor(df$time, c(paste0("pre.",x), paste0("pos.",x)))
  df
})

df.sum <- lapply(lvalues, FUN = function(x) {
  get_summary_stats(group_by(df[[x]],time)[,c("time","value")])
})
(do.call(rbind, df.sum))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(do.call(rbind, df.sum))
```

```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  df[[x]]$xj <- jitter(as.numeric(df[[x]]$time), amount=.1)
  df[[x]]$yj <- jitter(df[[x]]$value, amount = .01)
  
  pwc <- add_xy_position(wlx.md[[x]], fun = "mean_ci", step.increase=3.5)

  ggline(df.sum[[x]], x="time", y="mean", palette="jco", size=0.75) +
    geom_errorbar(aes_string(ymin="mean-ci", ymax="mean+ci"), width=0.1, size = 1) +
    geom_point(data = df[[x]], aes_string(x="xj",y="yj",colour="time"), size = 0.75) +
    geom_line(data = df[[x]], aes(x=xj, y =yj, group=ID), color = "gray", size = 0.25) +
    stat_pvalue_manual(pwc, hide.ns = F, label = "p = {p}") +
    ylab(paste0(x, "(ability)")) + xlab("")
})
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```


## Evaluating H2 (null)

H2 (null): Students who participated in scenarios with our proposed ITS and with training (experimental group) have the same mean score/ability in both the pre-test and post-test.


```{r include=FALSE}
sdat = dat[which(dat$Group == "Exp"),]

wlx.md <- lapply(lvalues, FUN = function(x) {
  pdat <- tidyr::pivot_longer(sdat[,c("ID",paste0("pre.",x),paste0("pos.",x))],
                              cols = ends_with(x), names_to = "time")
  add_significance(wilcox_test(pdat, value ~ time, paired = T,
                               alternative = "greater", detailed = T))
})

df = do.call(rbind, wlx.md)
(df = df[,c("group1","group2","n1","n2","estimate","statistic","p","p.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```

```{r include=FALSE}
df <- lapply(lvalues, FUN = function(x) {
  df = pivot_longer(sdat, cols = c(paste0("pre.",x), paste0("pos.",x)),
                    names_to = "time")
  df$time = factor(df$time, c(paste0("pre.",x), paste0("pos.",x)))
  df
})

df.sum <- lapply(lvalues, FUN = function(x) {
  get_summary_stats(group_by(df[[x]],time)[,c("time","value")])
})
(do.call(rbind, df.sum))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(do.call(rbind, df.sum))
```

```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  df[[x]]$xj <- jitter(as.numeric(df[[x]]$time), amount=.1)
  df[[x]]$yj <- jitter(df[[x]]$value, amount = .01)
  
  pwc <- add_xy_position(wlx.md[[x]], fun = "mean_ci", step.increase=3.5)

  ggline(df.sum[[x]], x="time", y="mean", palette="jco", size=0.75) +
    geom_errorbar(aes_string(ymin="mean-ci", ymax="mean+ci"), width=0.1, size = 1) +
    geom_point(data = df[[x]], aes_string(x="xj",y="yj",colour="time"), size = 0.75) +
    geom_line(data = df[[x]], aes(x=xj, y =yj, group=ID), color = "gray", size = 0.25) +
    stat_pvalue_manual(pwc, hide.ns = F, label = "p = {p}") +
    ylab(paste0(x, "(ability)")) + xlab("")
})
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```

### Sorocaba - SP :: Evaluating H2 (null)


```{r include=FALSE}
sdat = dat[which(dat$Group == "Exp" & dat$Town == "Sorocaba - SP"),]

wlx.md <- lapply(lvalues, FUN = function(x) {
  pdat <- tidyr::pivot_longer(sdat[,c("ID",paste0("pre.",x),paste0("pos.",x))],
                              cols = ends_with(x), names_to = "time")
  add_significance(wilcox_test(pdat, value ~ time, paired = T,
                               alternative = "greater", detailed = T))
})

df = do.call(rbind, wlx.md)
(df = df[,c("group1","group2","n1","n2","estimate","statistic","p","p.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```

```{r include=FALSE}
df <- lapply(lvalues, FUN = function(x) {
  df = pivot_longer(sdat, cols = c(paste0("pre.",x), paste0("pos.",x)),
                    names_to = "time")
  df$time = factor(df$time, c(paste0("pre.",x), paste0("pos.",x)))
  df
})

df.sum <- lapply(lvalues, FUN = function(x) {
  get_summary_stats(group_by(df[[x]],time)[,c("time","value")])
})
(do.call(rbind, df.sum))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(do.call(rbind, df.sum))
```

```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  df[[x]]$xj <- jitter(as.numeric(df[[x]]$time), amount=.1)
  df[[x]]$yj <- jitter(df[[x]]$value, amount = .01)
  
  pwc <- add_xy_position(wlx.md[[x]], fun = "mean_ci", step.increase=3.5)

  ggline(df.sum[[x]], x="time", y="mean", palette="jco", size=0.75) +
    geom_errorbar(aes_string(ymin="mean-ci", ymax="mean+ci"), width=0.1, size = 1) +
    geom_point(data = df[[x]], aes_string(x="xj",y="yj",colour="time"), size = 0.75) +
    geom_line(data = df[[x]], aes(x=xj, y =yj, group=ID), color = "gray", size = 0.25) +
    stat_pvalue_manual(pwc, hide.ns = F, label = "p = {p}") +
    ylab(paste0(x, "(ability)")) + xlab("")
})
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```



### Limoeiro - PE :: Evaluating H2 (null)


```{r include=FALSE}
sdat = dat[which(dat$Group == "Exp" & dat$Town == "Limoeiro - PE"),]

wlx.md <- lapply(lvalues, FUN = function(x) {
  pdat <- tidyr::pivot_longer(sdat[,c("ID",paste0("pre.",x),paste0("pos.",x))],
                              cols = ends_with(x), names_to = "time")
  add_significance(wilcox_test(pdat, value ~ time, paired = T,
                               alternative = "greater", detailed = T))
})

df = do.call(rbind, wlx.md)
(df = df[,c("group1","group2","n1","n2","estimate","statistic","p","p.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```

```{r include=FALSE}
df <- lapply(lvalues, FUN = function(x) {
  df = pivot_longer(sdat, cols = c(paste0("pre.",x), paste0("pos.",x)),
                    names_to = "time")
  df$time = factor(df$time, c(paste0("pre.",x), paste0("pos.",x)))
  df
})

df.sum <- lapply(lvalues, FUN = function(x) {
  get_summary_stats(group_by(df[[x]],time)[,c("time","value")])
})
(do.call(rbind, df.sum))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(do.call(rbind, df.sum))
```

```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  df[[x]]$xj <- jitter(as.numeric(df[[x]]$time), amount=.1)
  df[[x]]$yj <- jitter(df[[x]]$value, amount = .01)
  
  pwc <- add_xy_position(wlx.md[[x]], fun = "mean_ci", step.increase=3.5)

  ggline(df.sum[[x]], x="time", y="mean", palette="jco", size=0.75) +
    geom_errorbar(aes_string(ymin="mean-ci", ymax="mean+ci"), width=0.1, size = 1) +
    geom_point(data = df[[x]], aes_string(x="xj",y="yj",colour="time"), size = 0.75) +
    geom_line(data = df[[x]], aes(x=xj, y =yj, group=ID), color = "gray", size = 0.25) +
    stat_pvalue_manual(pwc, hide.ns = F, label = "p = {p}") +
    ylab(paste0(x, "(ability)")) + xlab("")
})
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```



```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```


## Evaluating H3 (null)

H3 (null): Students who participated in scenarios with our proposed ITS and with training (experimental group) have the same learning gain that students who participated in control groups.



```{r include=FALSE}
sdat = dat
kru.md <- lapply(lvalues, FUN = function(x) {
  kruskal.test(sdat, paste0("dif.",x), "Group")
})

df = do.call(rbind, lapply(kru.md, get.kruskal.table))
(df = df[,c("var","n","df","statistic","p","p.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```

```{r include=FALSE}
pwc.md <- lapply(lvalues, FUN = function(x) {
  kruskal.pwc(sdat, paste0("dif.",x), "Group")
})

df = do.call(rbind, lapply(pwc.md, get.kruskal.pwc.table))
(df = df[,c("var","group1","group2","n1","n2","estimate","statistic","p.adj","p.adj.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```


```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  stat.test <- pwc.md[[x]][[paste0("dif.",x)]]$Group %>% add_xy_position(x = "Group")
  ggboxplot(sdat, x = "Group", y = paste0("dif.",x),
            color = "Group", palette = c("#E7B800","#E799AA","#00AA55"),
            add = "jitter") +
    stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T) +
    ylab(paste0(x, "(dif)")) + xlab("") +
    labs(subtitle = get_test_label(kru.md[[x]][[paste0("dif.",x)]]$kt, detailed = T))
})
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```



```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```

### Subgroup analysis for Group:Town


```{r include=FALSE}
sdat = dat
sch.md <- lapply(lvalues, FUN = function(x) {
  scheirer.test(sdat, paste0("dif.",x), c("Group","Town"))
})

(df = do.call(rbind, lapply(sch.md, get.scheirer.table)))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```


```{r include=FALSE}
sdat = dat
pwc.md <- lapply(lvalues, FUN = function(x) {
  scheirer.pwc(sdat, paste0("dif.",x), between = c("Group","Town"))
})

df = do.call(rbind, lapply(pwc.md, get.scheirer.pwc.table))
(df = df[,c("var","Town","group1","group2","n1","n2","estimate","statistic","p.adj","p.adj.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```


```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  sch <- sch.md[[x]][[paste0("dif.",x)]]
  pwc <- pwc.md[[x]][[paste0("dif.",x)]]
  stat.test <-   pwc$Group %>% add_xy_position(x = "Group")
  
  ggboxplot(sdat, x = "Group", y = paste0("dif.",x),
            color = "Town", palette = c("#E700B8","#5500AA"),
            add = "jitter") +
    stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T) +
    ylab(paste0(x, "(dif)")) + xlab("")
})

```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```




### Subgroup analysis for Group:Quintiles


```{r include=FALSE}
sdat = dat
sch.md <- lapply(lvalues, FUN = function(x) {
  scheirer.test(sdat, paste0("dif.",x), c("Group", paste0("qtl.",x)))
})

(df = do.call(rbind, lapply(sch.md, get.scheirer.table)))
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```


```{r include=FALSE}
sdat = dat
pwc.md <- lapply(lvalues, FUN = function(x) {
  scheirer.pwc(sdat, paste0("dif.",x), between = c("Group",paste0("qtl.",x)))
})

df = do.call(rbind.fill, lapply(pwc.md, get.scheirer.pwc.table))
(df = df[,c(".y.","Group","group1","group2","n1","n2","estimate","statistic","p.adj","p.adj.signif")])
```

```{r echo=TRUE, purl=FALSE}
knitr::kable(df)
```


```{r include=FALSE}
plots <- lapply(lvalues, FUN = function(x) {
  sch <- sch.md[[x]][[paste0("dif.",x)]]
  pwc <- pwc.md[[x]][[paste0("dif.",x)]]
  stat.test <- pwc[[paste0("qtl.",x)]] %>% add_xy_position(x = "Group")
  
  ggboxplot(sdat, x = "Group", y = paste0("dif.",x),
            color = paste0("qtl.",x), palette = "jco") +
    stat_pvalue_manual(stat.test, tip.length = 0, hide.ns = T) +
    ylab(paste0(x, "(dif)")) + xlab("")
})

```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$score
```


```{r, dpi=300, fig.width=6, fig.height=6}
plots$irt.em.norm
```


